Map{R}educe in {MPI} for Large-scale Graph Algorithms

### 2011-02-23 paper/results.tex
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@815 3fc257bb-8550-0410-81b3-a5c103da83f7
Many redone figures so they look better in B&W.
git-svn-id: svn+ssh://software-srn.sandia.gov/svn/mapreduce/trunk@817 3fc257bb-8550-0410-81b3-a5c103da83f7

To give a rough sense of the effort involved to implement the various
MapReduce algorithms described in this section, we list the line
counts of the C++ codes used to perform the benchmarks.  Each code
makes calls to the MR-MPI library and implements the algorithm in the
indicated figure.  The line counts exclude comments and blank lines
which typically add about 30\% to the total.  They also exclude the
routines used to generate the R-MAT matrix input (except in the case
of the two R-MAT algorithms themselves) or process it into
upper-triangular form, since that is common to several of the
benchmarks.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
\hline
Algorithm & R-MAT & R-MAT++ & PageRank & Tri & CC & MIS & SSSP & SSSP++ \\
\hline
Lines of code & 208 & 216 & 603 & 367 & 453 & 393 & 394 & 448 \\
Figure & \ref{fig:rmat} & \ref{fig:rmat2} & \ref{fig:pr2} & \ref{fig:tri} & \ref{fig:cc} & \ref{fig:luby} & \ref{fig:sssp} & \ref{fig:sssp2} \\
\hline
\end{tabular}
\caption{Lines of code to implement each of the graph
  algorithms in the associated figures.}
\label{t:rmat}
\end{center}
\end{table}

@@

Finally, we demonstrate the scalability of our MR-MPI library to large
numbers of processors.  The library was used on Sandia's Redstorm and
Thunderbird parallel computers.  Redstorm is a large Cray XT3 with 2+
{GHz} dual/quad-core AMD Opteron processors and a custom interconnect
providing 9.6 GB/s of interprocessor bandwidth.  Thunderbird is a
large Linux cluster with 3.6 {GHz} dual-core Intel EM64T processors
connected by an Infiniband network.  Because these systems do not have
local disks for each processor, we selected a data set and page sizes
that fit in memory, so out-of-core operations were not needed.  For
these experiments, we used two R-MAT data sets with with $2^{25}$
vertices and $2^{28}$ edges, with parameters given in
Table~\ref{t:rmat}.  The ``nice'' parameters produce a less-skewed
sparsity pattern in the matrix than the ``nasty'' parameters, as
indicated by the maximum degree metric.  We ran both the PageRank and
Connected Components algorithms on these matrices.

>>>>

To give a rough sense of the effort involved to implement the various
MapReduce algorithms described in this section, we list in Table~\ref{t:linecount} the line
counts of the C++ codes used to perform the benchmarks.
Each code makes calls to the MR-MPI library
and implements the algorithm in the indicated figure.  The line counts
exclude comments and blank lines which typically add about 30\% to the
total.  They also exclude the routines used to generate the R-MAT
matrix input (except in the case of the two R-MAT algorithms
themselves) or process it into upper-triangular form, since that is
common to several of the benchmarks.

\begin{table}
\begin{center}
\begin{tabular}{|l|c|c|c|c|c|c|c|c|}
\hline
Algorithm & R-MAT & R-MAT++ & PageRank & Tri & CC & MIS & SSSP & SSSP++ \\
\hline
Lines of code & 208 & 216 & 603 & 367 & 453 & 393 & 394 & 448 \\
Figure & \ref{fig:rmat} & \ref{fig:rmat2} & \ref{fig:pr2} & \ref{fig:tri} & \ref{fig:cc} & \ref{fig:luby} & \ref{fig:sssp} & \ref{fig:sssp2} \\
\hline
\end{tabular}
\caption{Lines of code to implement each of the graph
  algorithms in the associated figures.}
\label{t:linecount}
\end{center}
\end{table}

@@

Finally, we demonstrate the scalability of our MR-MPI library to large
numbers of processors.  The library was used on Sandia's Redstorm and
Thunderbird parallel computers.  Redstorm is a large Cray XT3 with 2+
{GHz} dual/quad-core AMD Opteron processors and a custom interconnect
providing 9.6 GB/s of interprocessor bandwidth.  Thunderbird is a
large Linux cluster with 3.6 {GHz} dual-core Intel EM64T processors
connected by an Infiniband network.  Because these systems do not have
local disks for each processor, we selected a data set and page sizes
that fit in memory, so out-of-core operations were not needed.  For
these experiments, we used two R-MAT data sets with $2^{25}$ vertices
and $2^{28}$ edges, with parameters given in Table~\ref{t:rmat}.  The
``nice'' parameters produce a less-skewed sparsity pattern in the
matrix than the ``nasty'' parameters, as indicated by the maximum
degree metric.  We ran both the PageRank and Connected Components
algorithms on these matrices.
